---
title: "textanalysis_codes"
format: html
---

```{r}
#| echo: false
#| message: false

library(tidyverse)
library(ggplot2)
library(leaflet)
library(patchwork)
library(dplyr)
library(stringr)
library(lubridate)
library(tidytext)
library(textdata)
library(igraph)
library(ggraph)
library(magick)

jcmr <- read_csv("~/project-2/clean_jcmr.csv")
```

```{r}
#| include: false
# Adding specific stopwords. Here, we insert the "general" words, that we can  expect from any scientific article about CMR and fluff words that we would expect from any science journals (study, analysis, treatment, human, mechanisms, mode, findings, function, etc).

cmr_stopword <- c("study", "scientific", "high", "study", "increased", "induced", "levels", "expression", "potential", "treatment", "publishing", "related", "significantly", "accumulation", "showed", "related", "specific", "yrs", "age", "effect", "effects", "results", "analysis", "revealed", "human", "1", "2", "3", "group", "formation", "reduced", "function", "decreased", "model", "fat", "compared", "based", "size", "size", "stability", "assessment", "method", "clinical", "activity", "findings", "mechanisms", "energy", "exposure", "content", "properties", "development", "higher", "metabolic", "disease", "red", "white", "recovery", "cellular", "additional", "simultaneously", "emulsion", "molecular", "identified", "compounds", "composition", "mature", "site", "extracts", "significant", "including", "dependent", "independent", "patients", "background", "objectives", "recent", "studies", "information")

lexicon <-  rep("custom", times = length(cmr_stopword))

# Create a dataframe from the two vectors above
full_stopwords <- data.frame(cmr_stopword, lexicon)
names(full_stopwords) <- c("word", "lexicon")

# Add the dataframe to stop_words df that exists in the library stopwords
stop_words_fix <-  dplyr::bind_rows(stop_words, full_stopwords)

# For filtering (specifically) individual words
remove_word <- c("cmr", "cardiovascular", "data", "contrast", "images", "image", "imaging", "blood", "learning", "magnetic", "resonance", "flow", "approach"
)

# UNIGRAM: Replacing phrases into one word
replace_unigram <- c(
  "cardiovascular magnetic resonance" = "cmr",
  "magnetic resonance imaging" = "mri",
  "magnetic resonance angiography" = "mra",
  "dice similarity coefficient" = "dsc",
  "late gadolinium enhancement" = "lge",
  "computed tomography" = "ct",
  "four dimensional" = "4d",
  "three dimensional" = "3d",
  "left ventricular" = "lv",
  "left ventricule" = "lv",
  "right ventricule" = "rv",
  "deep learning" = "dl",
  "artificial intelligence" = "ai",
  "machine learning" = "ml",
  "positron emission tomography" = "pet",
  "interclass correlation coefficient" = "icc")

# BIGRAM:
replace_dict <- c(
  "cardiovascular magnetic resonance" = "cmr",
  "magnetic resonance imaging" = "mri",
  "magnetic resonance angiography" = "mra",
  "dice similarity coefficient" = "dsc",
  "late gadolinium enhancement" = "lge",
  "interclass correlation coefficient" = "icc")

# TRIGRAM:

remove_words <- c("mra", "mri", "cmr", "mbf", "lge", "lv", "dl", "lf", "la", "pc", "rv", "ai", "af", "cardiovascular", "wss", "dti","jcmr", "pet", "papers", "special")
filter_grams <- c(stop_words_fix$word, remove_words)
```

unigram: make a replace_phrases list.
we would love to have mri..mra.. lge.. dsc... icc

bigram: make a replace_phrases list: 4d... 3d...
potentially make a remove_words list that have 3 words combination. THAT WE ALREADY KNOW!
because we do not want "magnetic resonance" "cardiovascular magnetic", etc... bruh

trigram: make a remove_word list that will filter out one word abbreviation!


```{r}
# Finding most frequent (individual) words based on abstract
# Please update stop word list accordingly

unigram_plot <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  mutate(abstract = str_replace_all(abstract, replace_unigram)) |>
  unnest_tokens(output = word, input = abstract) |>
  anti_join(stop_words_fix) |>
  count(word, sort = TRUE) |>
  filter(word != "NA") |>
  filter(!word %in% c("cmr", "cardiovascular", "data", "contrast", "images", "image", "imaging", "blood", "learning", "magnetic", "resonance", "flow", "approach", "time", "measurements", "parameters", "single")) |>
  slice_max(n, n = 20, with_ties = FALSE)

p_uni <- unigram_plot |>
  ggplot(aes(reorder(word, n), n, fill = word)) +
  geom_col(width = 0.6, alpha = 0.9, show.legend = FALSE) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Most Frequent Words in Abstract",
       x = "Frequency", 
       y = "Unigram") +
   theme_minimal(base_size = 15) +
    theme(plot.title.position = "plot",
      plot.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_line(color = alpha("white", 0.15),
                                            linewidth = 0.3
      ))

abstract_bigram <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  mutate(abstract = str_replace_all(abstract, replace_dict)) |>
  unnest_tokens(bigram, abstract, token = "ngrams", n = 2) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2"), sep = " ") |>
  filter(!word1 %in% filter_grams,
         !word2 %in% filter_grams) |>
  filter(!is.na(word1) & !is.na(word2)) |>
  unite(bigram, word1, word2, sep = " ") |> 
  slice_max(n, n = 20, with_ties = FALSE)
  
bigram_plot <- abstract_bigram |>
  ggplot(aes(reorder(bigram, n), n, fill = bigram)) +
  geom_col(width = 0.6, alpha = 0.9, show.legend = FALSE) +
  coord_flip() +
  theme_minimal() +
  labs(title = "Most Frequent Two Words Combination in Abstract",
       x = "Frequency", 
       y = "Bigram") +
   theme_minimal(base_size = 15) +
    theme(
      plot.title.position = "plot",
      plot.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_line(
        color = alpha("white", 0.15),
        linewidth = 0.3
      ))

abstract_trigram <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  unnest_tokens(trigram, abstract, token = "ngrams", n = 3) |>
  filter(trigram != "NA") |>
  filter(!str_detect(trigram, "^\\d")) |>
  count(trigram, sort = TRUE) |>
  separate(trigram, c("word1", "word2", "word3"), sep = " ") |>
  filter(!word1 %in% filter_grams,
         !word2 %in% filter_grams,
         !word3 %in% filter_grams) |>
  filter(!is.na(word1) & !is.na(word2) & !is.na(word3)) |>
  unite(trigram, word1, word2, word3, sep = " ") |>
  slice_max(n, n = 20, with_ties = FALSE)

trigram_plot <- abstract_trigram |>
  ggplot(aes(reorder(trigram, n), n, fill = trigram)) +
  geom_col(width = 0.6, alpha = 0.9, show.legend = FALSE) +
  coord_flip(clip = "off") +
   scale_y_continuous(
    expand = expansion(mult = c(0, 0.15))
  ) +
  theme_minimal() +
  labs(title = "Most Frequent Three Words Combination in Abstract",
       x = "Frequency", 
       y = "Trigram") +
   theme_minimal(base_size = 15) +
    theme(
      plot.title.position = "plot",
      plot.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.background = element_rect(fill = "#fdfbf7", color = NA),
      panel.grid.major.y = element_blank(),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_line(
        color = alpha("white", 0.15),
        linewidth = 0.3
      ))

ggsave("uni.png", p_uni, width = 16, height = 6, dpi = 300, bg = "#fdfbf7")
ggsave("bi.png", bigram_plot, width = 8, height = 6, dpi = 300, bg = "#fdfbf7")
ggsave("tri.png", trigram_plot, width = 8, height = 6, dpi = 300, bg = "#fdfbf7")

imgs <- image_read(c(
  "uni.png",
  "bi.png",
  "tri.png"
))

gif <- imgs |>
  image_morph(frames = 12) |>
  image_animate(fps = 2)

image_write(
  gif,
  "ngrams.gif"
)
```


```{r}
unigram_plot <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  mutate(abstract = str_replace_all(abstract, replace_unigram)) |>
  unnest_tokens(output = word, input = abstract) |>
  anti_join(stop_words_fix) |>
  count(word, sort = TRUE) |>
  filter(word != "NA") |>
  filter(!word %in% c("cmr", "cardiovascular", "data", "contrast", "images", "image", "imaging", "blood", "learning", "magnetic", "resonance", "flow", "approach", "time", "measurements", "parameters", "single")) |>
  slice_max(n, n = 20, with_ties = FALSE) |>
  mutate(type = "Unigram") |>
  rename("term" = word)

abstract_bigram <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  mutate(abstract = str_replace_all(abstract, replace_dict)) |>
  unnest_tokens(bigram, abstract, token = "ngrams", n = 2) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2"), sep = " ") |>
  filter(!word1 %in% filter_grams,
         !word2 %in% filter_grams) |>
  filter(!is.na(word1) & !is.na(word2)) |>
  unite(bigram, word1, word2, sep = " ")

bigram_plot <- abstract_bigram |>
  slice_max(n, n = 20, with_ties = FALSE) |>
  mutate(type = "Bigram") |>
  rename("term" = bigram)

abstract_trigram <- clean_jcmr |>
  select(abstract) |>
  mutate(abstract = str_to_lower(abstract)) |>
  unnest_tokens(trigram, abstract, token = "ngrams", n = 3) |>
  filter(trigram != "NA") |>
  filter(!str_detect(trigram, "^\\d")) |>
  count(trigram, sort = TRUE) |>
  separate(trigram, c("word1", "word2", "word3"), sep = " ") |>
  filter(!word1 %in% filter_grams,
         !word2 %in% filter_grams,
         !word3 %in% filter_grams) |>
  filter(!is.na(word1) & !is.na(word2) & !is.na(word3)) |>
  unite(trigram, word1, word2, word3, sep = " ")

trigram_plot <- abstract_trigram |>
  slice_max(n, n = 20, with_ties = FALSE) |>
  mutate(type = "Trigram") |>
  rename("term" = trigram)

ngram_plot <- bind_rows(
  unigram_plot,
  bigram_plot,
  trigram_plot
)

ngram_plot <- ngram_plot |>
  group_by(type) |>
  arrange(desc(n), .by_group = TRUE) |>
  mutate(rank = row_number())

p <- ggplot(
  subset(ngram_plot, type == unique(type)[1]),
  aes(
    x = reorder(term, n),
    y = n,
    fill = term
  )
) +
  geom_col(show.legend = FALSE) +
  coord_flip()


```


```{r}
# Finding most frequent (individual) words based on title
# Please update stop word list accordingly

clean_jcmr |>
  select(title) |>
  mutate(title = str_to_lower(title)) |>
  unnest_tokens(output = word, input = title) |>
  anti_join(stop_words_fix) |>
  count(word, sort = TRUE) |>
  filter(word != "NA") |>
  slice_max(n, n = 20) |>
  ggplot(aes(fct_reorder(word, n), n)) +
  geom_col() +
  coord_flip()

title_bigram <- clean_jcmr |>
  unnest_tokens(bigram, title, token = "ngrams", n = 2) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2"), sep = " ") |>
  filter(!word1 %in% stop_words_fix$word,
         !word2 %in% stop_words_fix$word) |>
  filter(!is.na(word1) & !is.na(word2)) |>
  unite(bigram, word1, word2, sep = " ")

title_trigram <- clean_jcmr |>
  unnest_tokens(bigram, title, token = "ngrams", n = 3) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2", "word3"), sep = " ") |>
  filter(!word1 %in% stop_words_fix$word,
         !word2 %in% stop_words_fix$word,
         !word3 %in% stop_words_fix$word) |>
  filter(!is.na(word1) & !is.na(word2) & !is.na(word3)) |>
  unite(bigram, word1, word2, word3, sep = " ")
```


```{r}
# Finding most frequent (individual) words based on method
# Please update stop word list accordingly

clean_jcmr |>
  select(method) |>
  mutate(method = str_to_lower(method)) |>
    mutate(method = str_replace_all(
      method,
      "cardiovascular magnetic resonance",
      "cmr"
    )
  ) |>
  mutate(method = str_replace_all(
      method,
      "magnetic resonance imaging",
      "mri"
    )
  ) |>
    mutate(method = str_replace_all(
      method,
      "dice similarity coefficient",
      "dsc"
    )
  ) |>
  mutate(method = str_replace_all(
      method,
      "late gadolinium enhancement",
      "lge"
    )
  ) |>
    mutate(method = str_replace_all(
      method,
      "magnetic resonance angiography",
      "mra"
    )
  ) |>
  unnest_tokens(output = word, input = method) |>
  anti_join(stop_words_fix) |>
  count(word, sort = TRUE) |>
  filter(word != "NA") |>
  slice_max(n, n = 20) |>
  ggplot(aes(fct_reorder(word, n), n)) +
  geom_col() +
  coord_flip()

method_bigram <- clean_jcmr |>
  unnest_tokens(bigram, method, token = "ngrams", n = 2) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2"), sep = " ") |>
  filter(!word1 %in% stop_words_fix$word,
         !word2 %in% stop_words_fix$word) |>
  filter(!is.na(word1) & !is.na(word2)) |>
  unite(bigram, word1, word2, sep = " ")

method_trigram <- clean_jcmr |>
  select(method) |>
  mutate(method = str_to_lower(method)) |>
  unnest_tokens(bigram, method, token = "ngrams", n = 3) |>
  filter(bigram != "NA") |>
  filter(!str_detect(bigram, "^\\d")) |>
  count(bigram, sort = TRUE) |>
  separate(bigram, c("word1", "word2", "word3"), sep = " ") |>
  filter(!word1 %in% stop_words_fix$word,
         !word2 %in% stop_words_fix$word,
         !word3 %in% stop_words_fix$word) |>
  filter(!is.na(word1) & !is.na(word2) & !is.na(word3)) |>
  unite(bigram, word1, word2, word3, sep = " ")

```

unigram: make a replace_phrases list.
we would love to have mri..mra.. lge.. dsc... icc


bigram: make a replace_phrases list: 4d... 3d...
potentially make a remove_words list that have 3 words combination. THAT WE ALREADY KNOW!
because we do not want "magnetic resonance" "cardiovascular magnetic", etc... bruh

trigram: make a remove_word list that will filter out one word abbreviation!

then. make a gganimate out of this! solid ! ! !
